Looking for a Signal in the Noise: Revisiting Obesity and the Microbiome

### 2016-05-23 submission/Sze_Obesity_PeerJ_2016.Rmd
modifying data tables used pt1

demographics <- read.csv("results/tables/denovodemographicsTable.csv")
OverallPValue <- read.csv("results/tables/denovoOverallPTable.csv")
ShannonRRTable <- read.csv("results/tables/denovoShannonRRTable.csv")
BFRatioRRTable <- read.csv("results/tables/denovoBFRatioRRTable.csv")
ZScoreCombinedData <- read.csv("results/tables/denovoCombinedData.csv")
ZScoreTurnbaughData <- read.csv("results/tables/denovoTurnbaughData.csv")
AUCRFData <- read.csv("results/tables/denovoAUCRFDataTable.csv")
PowerTable <- read.csv("results/tables/denovoPowerTable.csv")
ModelledPower1PerDiff <- read.csv("results/tables/denovoModelled1PerDiff.csv")
ModelledPower5PerDiff <- read.csv("results/tables/denovoModelled5PerDiff.csv")
ModelledPower10PerDiff <- read.csv("results/tables/denovoModelled10PerDiff.csv")
ModelledPower15PerDiff <- read.csv("results/tables/denovoModelled15PerDiff.csv")
ActualDiff <- read.csv("results/tables/denovoActualDiff.csv")
PowerModelHRR <- read.csv("results/tables/denovoPowerModelHRR.csv")
PowerModelBFRR <- read.csv("results/tables/denovoPowerModelBFRR.csv")
SimulatedN_H <- read.csv("results/tables/denovoSimulatedN_H.csv")
SimulatedN_BF <- read.csv("results/tables/denovoSimulatedN_BF.csv")
RRSimNNeededH <- read.csv("results/tables/denovoRRSimNNeededH.csv")
RRSimNNeededBF <- read.csv("results/tables/denovoRRSimNNeededBF.csv")

>>>>

alpha_tests.summary <- read.table("../data/process/alpha_tests.summary", header=T)
alpha_composite.summary <- read.table("../data/process/alpha_composite.summary")
alpha_power.obs <- read.table("../data/process/alpha_power.observed", 
                              header = T, row.names = 1)
alpha_power.predicted <- read.table("../data/process/alpha_power.predicted", 
                                    header = T)

beta_tests.summary <- read.table("../data/process/beta_tests.summary", 
                                 header=T, row.names = 1)
rand_forest.genus.roc_data <- read.table("../data/process/random_forest.genus.roc_data", header=T)

rand_forest.genus.summary <- read.table("../data/process/random_forest.genus.summary", 
                                        header = T, row.names = 1)

rand_forest.genus.train_test <- 
  read.table("../data/process/random_forest.genus.train_test", header = T)

rand_forest.otu.roc_data <- 
  read.table("../data/process/random_forest.otu.roc_data", header = T)

rand_forest.otu.summary <- 
  read.table("../data/process/random_forest.otu.summary", 
             header = T, row.names = 1)

RR_composite <- read.table("../data/process/relative_risk.composite", header = T)
RR_summary <- read.table("../data/process/relative_risk.summary", header = T)
RR_pow.obs <- read.table("../data/process/rr_power.observed", 
                         header = T, row.names = 1)
RR_pow.pred <- read.table("../data/process/rr_power.predicted", header = T)

# Hold on to these for now as I update the rest of the rmd.
demographics <- read.csv("results/tables/denovodemographicsTable.csv")
OverallPValue <- read.csv("results/tables/denovoOverallPTable.csv")
ShannonRRTable <- read.csv("results/tables/denovoShannonRRTable.csv")
BFRatioRRTable <- read.csv("results/tables/denovoBFRatioRRTable.csv")
ZScoreCombinedData <- read.csv("results/tables/denovoCombinedData.csv")
ZScoreTurnbaughData <- read.csv("results/tables/denovoTurnbaughData.csv")
AUCRFData <- read.csv("results/tables/denovoAUCRFDataTable.csv")
PowerTable <- read.csv("results/tables/denovoPowerTable.csv")
ModelledPower1PerDiff <- read.csv("results/tables/denovoModelled1PerDiff.csv")
ModelledPower5PerDiff <- read.csv("results/tables/denovoModelled5PerDiff.csv")
ModelledPower10PerDiff <- read.csv("results/tables/denovoModelled10PerDiff.csv")
ModelledPower15PerDiff <- read.csv("results/tables/denovoModelled15PerDiff.csv")
ActualDiff <- read.csv("results/tables/denovoActualDiff.csv")
PowerModelHRR <- read.csv("results/tables/denovoPowerModelHRR.csv")
PowerModelBFRR <- read.csv("results/tables/denovoPowerModelBFRR.csv")
SimulatedN_H <- read.csv("results/tables/denovoSimulatedN_H.csv")
SimulatedN_BF <- read.csv("results/tables/denovoSimulatedN_BF.csv")
RRSimNNeededH <- read.csv("results/tables/denovoRRSimNNeededH.csv")
RRSimNNeededBF <- read.csv("results/tables/denovoRRSimNNeededBF.csv")
